---
title: "README"
author: "Christiaan van Rensburg, Alexander Cawood, Marette Theron"
date: "9/13/2019"
output: rmarkdown::github_document
bibliography: inst/REFERENCES.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction

## Install Instructions

Ensure you have the `githubinstall` package installed and the `devtools` package installed
```{}
install.packages('devtools')
install.packages('githubinstall')
```

```{r}
library('Rfrenz')
```

### Generating Test Data
```{r generate data}

r1 <- matrix(c(0,1,0,1,0,
              0,0,1,1,0,
              1,0,0,1,1,
              0,1,0,0,1,
              0,1,0,1,0),nrow=5, ncol=5)
r2 <- matrix(c(0,1,1,1,0,
              0,0,1,1,0,
              1,0,0,1,0,
              1,1,0,0,1,
              1,1,0,1,0),nrow=5, ncol=5)
r3 <- matrix(c(0,1,1,1,0,
              1,0,1,1,0,
              1,1,0,0,0,
              0,1,0,0,1,
              1,1,0,1,0),nrow=5, ncol=5)
r4 <- matrix(c(0,1,0,1,0,
              1,0,1,1,1,
              1,0,0,1,1,
              0,1,0,0,0,
              0,0,0,1,0),nrow=5, ncol=5)
r5 <- matrix(c(NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA),nrow=5, ncol=5)

list_respondent <- list(r1,r2,r3,r4,r5)

```


## The Rfrenz function
This function generates a criterion (true) network given all the perceptions perceived in a network. The criterion network is then compared to all perceptions in order to determine th similarity between a respondent and thier perception of the network.

#### Arguments 
`dat` - A list of socio matricies that represent respondents.
`criterion` - A true (criterion) netwrok of the socio matricies to be computed.
`accuracy` - An accuracy measure to be computed
```{r}

rfrenz_acc(list_respondent, criterion = "ILAS", accuracy="s14")

```
#### Values
The `rfrenz_acc` function returns a list of 2 items. The first is the criterion network. The second is a dataframe containing an accuracy score for each respondent

## The Data 

### Get Data

The get_data function can be used to read in data from a directory containing comma seperated binary values in a text files, where each text file represents a respondent.
```{ Get Data}

get_data(path, save = FALSE, path_out)

```

### Formating Data
Remove/Replace Missing Slices
```{r Formatting Data}
formatting_data(list_respondent, option = "replace")
```

### Mock Data


## Criterion

Criterion (also called true or actual) networks are representative of the notion of shared or common perceptions of social structures from all observers within a network. Various different algorithms exist to derive these actual networks namely: Local Aggregate Structures (LAS), Consensus Structures and Expert Structures [@Krackhardt1987a][@Cornelissen2019].

#### Local Aggregate Structures (LAS)

LAS is suitable in a context to generate which suggests that only the individuals directly involved in the relation determine the existence of the relation.

##### RLAS: Row-Dominated LAS
An RLAS criterion is created by determining whether or not the perceiver observes the relationship to exist, even though the receiver does not always necessarily deem it to exist [@Krackhardt1987a]. Thus, the sender of the relationship will be assumed as correct. Function used: consensus from the SNA package [@Butts2016].

##### CLAS: Column-Dominated LAS.
CLAS is created by determining whether or not the receiver of the relation perceives the relation to exist. Thus, the receiver of the relationship will be assumed as correct. Function used: consensus from the SNA package [@Butts2016].

##### ILAS: Intersection LAS
ILAS criterion networks are created by determining whether or not both respondents perceive the tie to exist. Thus, both respondents have to agree on the relationship in order for it to exist [@Krackhardt1987a]. Function used: consensus from the SNA package [@Butts2016].

##### ULAS: Union LAS
ULAS defines relations to exist if at least one of the respondents involved in the relation perceives it to exist [@Krackhardt1987a]. Function used: consensus from the SNA package [@Butts2016].

#### Consensus Structures

##### GA: Global Aggregate
Using Global Aggregate to generate actual networks is not so much focused on who perceived a specific relations, but rather how many perceived that relation. This is done by taking the sum of relationships that exists for each observer.

##### GAT: Global Aggregate with a threshold
The threshold is set to measure the proportion of members that perceive a relation between the sender and receiver of the relationship. This corresponds to a “median response” notion of creating an actual network. Function used: consensus from the SNA package [@Butts2016].

##### GAV: Global Aggregate (valued)
To gain a clearer understanding of the global perception of a relation, one could make use of proportions rather than showing only the presence or absence of a perceived relation (i.e. the GAT method). Thus, this method shows which percentage of observers perceived the relationship.

#### Expert Structures

##### SR: Single Reweight
The reweight method takes consensus structure to create an initial criterion network. The reweight method is then applied to give a more accurate representation of the perceptions in the network. This is done is by performing consensus structure reduction on the data again but with different perceivers weighted according to their accuracy in perceiving relations in original criterion network. The single reweight method is when there is only one additional reduction done using the reweighted nodes. Function used: consensus from the SNA package [@Butts2016].

##### IR: Iterative Reweight
Similar to Single Reweight except this method applies multiple reductions to weigh perceivers differently in each iteration. This can be useful when there is a disconnect between different perceptions which results in relations which are not accurate or don't exist. IR tries to find the most accurate perceivers in the network in order to give their perceptions of relations more validity when determining the criterion network. Function used: consensus from the SNA package [@Butts2016].

##### RB: Romney Batchelder
Similar to Single Reweight method but with an exception to the motivation. Romney Batchelder theory's motivation lies in the measurement of shared beliefs in a group. The criterion is built on the “cultural competency” weighted perceptions. Measuring “cultural competency” of respondents is done by determining the correlation between the responses of each individual and the aggregated responses of the group.

##### PCA: Principal Component Analysis.
The PCA method for generating actual networks uses the first component of a network. PCA extracts shared themes among all the respondents within a network [@Butts2016]. PCA reduces the dimensions and relationships considered a data set while still maintaining the most important information within it. Function used: consensus from the SNA package [@Butts2016].

##### BAY: Bayesian
Network accuracy model method can be used to generate the criterion network given the probability of false positives and false negatives. For more information see Bayesian. Function used: consensus from the SNA package [@Butts2016].

### Get Criterion

This function generates a criterion (true) network given all the perceptions perceived in a network. Several algorithms for determining criterion networks are available to best suit the context of the network.

#### Arguments:
`dat` - A socio-matrix containing all of the perceptions of a network
`criterion` - The criterion network needed to be generated (“RLAS”, “CLAS”, “ILAS”, “ULAS”, “GA”, “GAT”, “GAV”, “SR”, “IR”, “PCA”, “RB”, “BAY”)

#### Usage:
```{r Get Criterion}
crit <- get_criterion(list_respondent, criterion='RLAS')
crit

```

#### Values:
The function returns a socio-matrix representing the Criterion ('true') Network structure
#### Example:


## Accuracy 

The purpose of this package is to get the accuracy scores for each respondent in a social network based on their perception of the network. This is done by checking the similarity between their perception and a criterion network (i.e., a network that best represents the relations in a network).

#### Interpersonal Accuracy
##### Pearson Correlation
The Pearson correlation test is done using a function from the SNA package called `gcor`. The SNA package states that “gcor” function is used to find the product-moment correlation between adjacency matrices [@Butts2016]. The “gcor” is a specialised form of a standard “cor” correlation. The ”gcor” function focuses more on graph data. Scores larger than 0 show a positive correlation whereas scores below 0 show a negative correlation.

##### Spearman Correlation
The Spearman correlation test is performed using the `cor.test` function from the stats package. The estimate value is extracted from the results of the test. This value represents the similarity score computed from the correlation. According to the Stats package the rho statistic is used to compute the estimate value of the ranked based measure of association [@DeNooy2016]. A Spearman correlation test is best suited for data that can be ranked. Scores larger than 0 show a positive correlation whereas scores below 0 show a negative correlation.

##### Jaccard Correlation
The Jaccard similarity coefficient is performed using the `jaccard` function that is found in the Jaccard package. This function will result in a number between 1 and 0. The closer the value is to 1 the higher the similarity is between the two matrices. The Jaccard similarity coefficient is used in social science as it shows the occurrences of agreements between binary sets of data [@Marineau2016a].

##### Kendall Rank Correlation
The Kendall rank correlation is performed using the `kendall` function that is found in the Kendall package. The Kendall rank correlation or more commonly known as Kendall's tau, is a correlation tool used to measure the ordinal association between two measured variables [@Kendall1938]. The “Kendall” function computes a p-value and if it determined to be significant such that variables are dependent, and therefore there are ties. Then it will checks the similarity between these variables. The Kendall Tau statistic is extracted from the results of this function.

##### S14 Similarity Index
The s14 similarity index is performed using the `s14` function that is found in the cssTools package. The s14 function computes the similarity between the two square matrices. S14 is useful for network data as it shows appropriate sensitivity to small changes and does not distort at extremes [@Gower1986].

##### MRQAP with Double-Semi-Partialing (DSP)
MRQAP with DSP is performed using the `mrqap.dsp` function that is found in the Asnipe package. This function computes the regression coefficient using the DSP method. The method randomises the p-value with 1000 permutation in order to determine if the matrices are dependent or independent [@Dekker2003].

##### Cohens Kappa
The Cohens Kappa coefficient can be determined using the `cohen.kappa` function that can be found in the psych package. This accuracy measure takes the possibility of chance into account (i.e., someone could have merely guessed about a relationship within a given network and the measure takes that probability into account) (Cohen 1960). Target accuracy measures refer to how accurate a perceiver's agreement would be towards a certain target, where the target would be the relationship between i and j [@Neal2016].

##### Local Accuracy
The local accuracy is computed by comparing a person's perceptions to a Row dominated local aggregate structure (RLAS). local accuracy tries to see how accurate a person is at knowing the perceptions in a social network based on how they think the people in that network perceive them [@Casciaro1999]. A pearson correlation is performed between a row of a person's perceptions and a row of the RLAS criterion.

##### Dyadic Accuracy
Dyadic accuracy looks at how accurately an individual can perceive a possible dyadic relation between two individuals. To do this it takes one person perceptions and measures its perception of dyadic relations according to the “true” network [@Bondonio1998].

#### Intermediate Accuracy
##### Triadic (Pearson, Spearman, Distance)
The triadic accuracy compares the triadic structure of the criterion network and the respondent by means of either a Pearson correlation, Spearman's rank correlation, or Euclidean distance measure. This approach was proposed by @Frenz2019 as a means to compare the degree of similarity between the triad census of the actual social network and the triad census of a respondents cognitive slice.

#### Structural Accuracy
##### Structural Correlation (gscor)
The structural correlation between two or more graphs can be determined using the `gscor` function found in the SNA package. The gscor function finds the product-movement structural correlation. This indicates that it looks at the structure of each network and determines how similar the structure is as opposed to if specific ties were similar between nodes (Butts and Carley 2001). The node labels in the network are permutated in order to determine how similar the structure is to the true network [@Butts2001].

### Get Accuracy

The purpose of this function is to get the accuracy scores for each respondent in a social network based on their perception of the network. This is done by checking the similarity between their perception and a criterion network (i.e., a network that best represents the relations in a network).

#### Arguments
`dat` - A list of socio matrices that represent respondents.
`criterion` - A sociomatrix that represents the criterion network (i.e., a network that best represents the relations in a network) that is computed from all respondents.
`acc` - The name of the accuracy measure to be computed. Options: “pearson”, “spearman”, “jaccard”, “kendall”, “s14”, “mrqap”, “gscor”, “CohenK”, “local”, “triadic pearson”, “triadic spearman”, “triadic distance”.
`criterion_type` - The name of the criterion that has been used.

```{r Get Accuracy}

acc_df<- get_accuracy(list_respondent, crit, acc = "pearson", criterion_type = "RLAS")

acc_df

```

#### Values
A dataframe of respondents and there accuracy scores.
#### Example:

## Plotting

### Rfrenz plot
This function can be used to quickly plot a summary of the get_crit() and get_accuracy() functions in one place.
#### Arguments
`crit` - criterion network returned after get_criterion() is run. the crit is used to plot a criterion network.

`accuracy_df` - accuracy score dataframe that is return after get_accruacy() from Rfrenze is run. the accruacy_df is used to plot a boxplot summarising the data

`criterion` - default="RLAS". the criterion name of the criterion being past in crit. is used as a titile for the graph.

```{r Rfrenz plot}
frenz_plot(crit, acc_df,criterion="RLAS")
```

## Conclusion

# References
